Tutorial 2b

### 2025-07-13 Tutorial_2a.Rmd
small corrections
update Figures 3 and 4

Tutorial 2a shows various ways to fit Bayesian binary regression models to discrete time-to-event data (section 3). The data are taken from the first experiment of @panisWhatShapingRT2016, but using only the no-mask trials (with factor prime = blank, congruent, or incongruent). We performed some prior predictive checks to determine the prior distributions we will employ (section 8). We compare models using WAIC and LOO (section 4), and interpret parameter estimates for one model (section 5). 
We also plot the logit and cloglog link functions (section 6), and illustrate how various prior distributions for an intercept on the logit and cloglog scales look on the original probability (i.e., hazard) scale (section 7).

@@

Prepare the data file, and specify priors. The skew-normal prior is set for each grand intercept on the cloglog scale, and reflects our prior belief that higher hazard values (above .5) are less likely than lower values (below .5). This prior is plotted in row F of Supplementary Figure 2 (section E in the Supplemental Material).
A prior predictive check is performed in section 8.1.

@@

# plot
p_tidy_fixed <- ggplot(tidy_fixed, aes(x = timebin, y = value, fill=condition)) +  
  stat_halfeye(point_interval="median_qi", 
               .width = c(0.80,0.95),
               alpha=0.7) +
  labs(title = 'Posterior distributions for population-level\neffects in Model M1i',
       x = "time bin", y = "cloglog-hazard") +
  scale_fill_brewer(palette = "Dark2") +
  scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
   theme(axis.text.x = element_text(angle=90)) +
  facet_wrap(~condition)
p_tidy_fixed
```

@@

```{r epred-grand-plot}
 p1 <- ggplot(epreds_grand, aes(x=timebin, y=.epred, 
                          fill=prime, color=prime)) +
    stat_lineribbon(aes(linetype=prime),
                    point_interval="median_qi",
                    .width=c(.8,.95),
                    alpha = 0.5) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), 
                     breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,.6)) +
    labs(x = "time bin", y = "predicted hazard")

@@

ggplot(aes(x=timebin, y=haz, 
           fill=condition, color=condition)) +
    stat_lineribbon(aes(linetype=condition),
                    point_interval="median_qi",
                    .width=.95,
                    alpha = 0.5) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,.6)) +
    labs(x = "time bin", y = "predicted hazard") 
```

@@

```{r epred-pid-plot}
p2 <- ggplot(epreds_pid, aes(x=timebin, y=.epred, 
                       fill=prime, color=prime)) +
    stat_lineribbon(aes(linetype=prime),
                    point_interval="median_qi",
                    .width=c(.8,.95),
                    alpha = 0.5) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,1)) +
    labs(x = "time bin", y = "predicted hazard") +
   # ggtitle("Each participant (N = 6)") +
    facet_wrap(~pid, ncol=3)

@@

```{r epred-grand-diff-plot}
 p11 <- ggplot(epreds_grand_diffs, aes(x=timebin, y=diff, 
                       fill=contrast)) +
  stat_lineribbon(alpha = 0.4, 
                  point_interval = "mean_qi",
                  .width=c(.8,.95)) +
  geom_hline(yintercept = 0, 
             color = "red", 
             lty = 3) +
  scale_y_continuous(limits=c(-0.5,0.3)) +
  scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
  scale_fill_manual(values=c("#D95F02FF", "#7570B3FF")) +
  theme(axis.text.x = element_text(angle=90)) +
  labs(x = "time bin", y = "difference in predicted hazard") +
  #ggtitle("Grand average marginal effect") +
  facet_wrap(~contrast)

@@

```{r epred-pid-diff-plot}
 p22 <- ggplot(epreds_pid_diffs, aes(x=timebin, y=diff, 
                              fill=contrast, color=contrast)) +
    stat_lineribbon(aes(linetype=contrast),
                    alpha = 0.4, 
                    point_interval = "mean_qi",
                    .width=c(.8,.95)) +
    #stat_halfeye(point_interval = "mean_qi",.width=c(.8,.95)) +
    geom_hline(yintercept = 0, color = "red", lty = 3) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(-0.6,0.6)) +
    labs(x = "time bin", y = "difference in predicted hazard") +
    #ggtitle("Subject-specific AMEs") +
    facet_wrap(~pid, ncol=3)

@@

(p11_theme / p22) +
    plot_annotation(tag_levels = 'A') +
   # plot_layout(guides = "collect",
  #              axes = "collect_x") & 
    theme(legend.position = "bottom")
```

@@

(p_tidy_fixed / p1 / p11) +
    plot_annotation(tag_levels = 'A') +
   # plot_layout(guides = "collect",
  #              axes = "collect_x") & 
    theme(legend.position = "bottom")

```

@@

If we want to study the population-level effect of prime type on hazard, uncontaminated by inter-individual differences, we can base our conclusion on Figure 7A. The contrast "congruent minus blank" was estimated to be 0.09 hazard units in bin 6 (95% CrI = [0.02, 0.17]), and 0.14 hazard units in bin 7 (95% CrI = [0.04, 0.25]). For the other bins, the 95% credible interval contained zero.
The contrast "incongruent minus blank" was estimated to be 0.09 hazard units in bin 6 (95% CrI = [0.01, 0.21]), -0.19 hazard units in bin 9 (95% CrI = [-0.31, -0.06]), -0.27 hazard units in bin 10 (95% CrI = [-0.45, -0.04]), and -0.23 hazard units in bin 11 (95% CrI = [-0.40, -0.03]). For the other bins, the 95% credible interval contained zero. Note that we could also have calculated hazard ratios instead of hazard differences.

There are thus two phases of performance for the average person between 200 and 600 ms after target onset. In the first phase, the addition of a congruent or incongruent prime stimulus increases the hazard of response occurrence compared to blank prime trials in the time period (200, 240]. In the second phase, only the incongruent prime decreases the hazard of response occurrence compared to blank primes, in the time period (320,440]. The sign of the effect of incongruent primes on the hazard of response occurrrence thus depends on how much waiting time has passed since target onset.

@@

If we want to focus more on inter-individual differences, we can study the subject-specific differences in hazard in Figure 7B. Note that three participants (1, 2, and 3) show a negative difference for the contrast "congruent minus incongruent" in bin (360,400] -- subject 2 also in bin (320,360].

@@

Interestingly, all subjects show a tendency in their mean difference (congruent minus blank) to "dip" around that time (Figure 9). Therefore, future modeling efforts could incorporate the trial number into the model formula, in order to also study how the effects of prime type on hazard change on the long experiment-wide time scale, next to the short trial-wide time scale. In Tutorial_2a.Rmd we provide a number of model formula that should get you going.

>>>>

Tutorial 2a shows various ways to fit Bayesian binary regression models to discrete time-to-event data (section 3). The data are taken from the first experiment of @panisWhatShapingRT2016, but using only the no-mask trials (with factor prime = blank, congruent, or incongruent). We performed some prior predictive checks to determine the prior distributions we will employ (section 8). We compare models using WAIC and LOO (section 4), and interpret parameter estimates for one model (section 5). 
We also plot the logit and cloglog link functions (section 6), and illustrate how various prior distributions for an intercept on the logit and cloglog scales look on the original probability (i.e., discrete-time hazard) scale (section 7).

@@

Prepare the data file, and specify priors. The skew-normal prior is set for each grand intercept on the cloglog scale, and reflects our prior belief that higher hazard values (above .5) are less likely than lower values (below .5). This prior is plotted in row F of Supplementary Figure 3 (section F in the Supplemental Material).
A prior predictive check is performed in section 8.1.

@@

# plot
p_tidy_fixed <- ggplot(tidy_fixed, aes(x = timebin, y = value, fill=condition)) +  
  stat_halfeye(point_interval="median_qi", 
               .width = c(0.80,0.95),
               alpha=0.7) +
  labs(title = 'Posterior distributions for population-level\neffects in Model M1i',
       x = "time bin (upper bound in ms)", y = "cloglog-hazard") +
  scale_fill_brewer(palette = "Dark2") +
  scale_x_discrete(labels = c(6:15)*40, breaks = 6:15) +
  theme(axis.text.x = element_text(angle=90)) +
  facet_wrap(~condition)
p_tidy_fixed
```

@@

```{r epred-grand-plot}
 p1 <- ggplot(epreds_grand, aes(x=timebin, y=.epred, 
                          fill=prime, color=prime)) +
    stat_lineribbon(aes(linetype=prime),
                    point_interval="median_qi",
                    .width=c(.8,.95),
                    alpha = 0.5) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = c(6:15)*40, 
                     breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,.6)) +
    labs(x = "time bin (upper bound in ms)", y = "predicted hazard")

@@

ggplot(aes(x=timebin, y=haz, 
           fill=condition, color=condition)) +
    stat_lineribbon(aes(linetype=condition),
                    point_interval="median_qi",
                    .width=.95,
                    alpha = 0.5) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = c(6:15)*40, breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,.6)) +
    labs(x = "time bin (upper bound in ms)", y = "predicted hazard") 
```

@@

```{r epred-pid-plot}
p2 <- ggplot(epreds_pid, aes(x=timebin, y=.epred, 
                       fill=prime, color=prime)) +
    stat_lineribbon(aes(linetype=prime),
                    point_interval="median_qi",
                    .width=c(.8,.95),
                    alpha = 0.5) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = c(6:15)*40, breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,1)) +
    labs(x = "time bin (upper bound in ms)", y = "predicted hazard") +
    facet_wrap(~pid, ncol=3)

@@

```{r epred-grand-diff-plot}
 p11 <- ggplot(epreds_grand_diffs, aes(x=timebin, y=diff, 
                       fill=contrast)) +
  stat_lineribbon(alpha = 0.4, 
                  point_interval = "mean_qi",
                  .width=c(.8,.95)) +
  geom_hline(yintercept = 0, 
             color = "red", 
             lty = 3) +
  scale_y_continuous(limits=c(-0.5,0.3)) +
  scale_x_discrete(labels = c(6:15)*40, breaks = 6:15) +
  scale_fill_manual(values=c("#D95F02FF", "#7570B3FF")) +
  theme(axis.text.x = element_text(angle=90)) +
  labs(x = "time bin (upper bound in ms)", y = "difference in predicted hazard") +
  facet_wrap(~contrast)

@@

```{r epred-pid-diff-plot}
 p22 <- ggplot(epreds_pid_diffs, aes(x=timebin, y=diff, 
                              fill=contrast, color=contrast)) +
    stat_lineribbon(aes(linetype=contrast),
                    alpha = 0.4, 
                    point_interval = "mean_qi",
                    .width=c(.8,.95)) +
    #stat_halfeye(point_interval = "mean_qi",.width=c(.8,.95)) +
    geom_hline(yintercept = 0, color = "red", lty = 3) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = c(6:15)*40, breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(-0.6,0.6)) +
    labs(x = "time bin (upper bound in ms)", y = "difference in predicted hazard") +
    facet_wrap(~pid, ncol=3)

@@

(p11_theme / p22) +
    plot_annotation(tag_levels = 'A') +
    theme(legend.position = "bottom")
```

@@

(p_tidy_fixed / p1 / p11) +
    plot_annotation(tag_levels = 'A') +
    theme(legend.position = "bottom")
```

@@

If we want to study the population-level effect of prime type on hazard, uncontaminated by inter-individual differences, we can base our conclusion on the population-level contrasts. The contrast "congruent minus blank" was estimated to be 0.09 hazard units in bin 6 (95% CrI = [0.02, 0.17]), and 0.14 hazard units in bin 7 (95% CrI = [0.04, 0.25]). For the other bins, the 95% credible interval contained zero.
The contrast "incongruent minus blank" was estimated to be 0.09 hazard units in bin 6 (95% CrI = [0.01, 0.21]), -0.19 hazard units in bin 9 (95% CrI = [-0.31, -0.06]), -0.27 hazard units in bin 10 (95% CrI = [-0.45, -0.04]), and -0.23 hazard units in bin 11 (95% CrI = [-0.40, -0.03]). For the other bins, the 95% credible interval contained zero. Note that we could also have calculated hazard ratios instead of hazard differences.

There are thus two phases of performance for the average person between 200 and 600 ms after target onset. In the first phase, the addition of a congruent or incongruent prime stimulus increases the hazard of response occurrence compared to blank prime trials in the time period 200-240 ms. In the second phase, only the incongruent prime decreases the hazard of response occurrence compared to blank primes, in the time period 320-440 ms. The sign of the effect of incongruent primes on the hazard of response occurrrence thus depends on how much waiting time has passed since target onset.

@@

If we want to focus more on inter-individual differences, we can study the subject-specific contrasts. Note that three participants (1, 2, and 3) show a negative difference for the contrast "congruent minus incongruent" in bin 400 -- subject 2 also in bin 360.

@@

Interestingly, all subjects show a tendency in their mean difference (congruent minus blank) to "dip" around that time. Therefore, future modeling efforts could incorporate the trial number into the model formula, in order to also study how the effects of prime type on hazard change on the long experiment-wide time scale, next to the short trial-wide time scale. In Tutorial_2a.Rmd we provide a number of model formula that should get you going.

### 2025-07-13 Tutorial_2b.Rmd
update Figures 3 and 4

# plot
p_tidy_fixed_ca <- ggplot(tidy_fixed_ca, aes(x = timebin, y = value, fill=condition)) +  
  stat_halfeye(point_interval = "median_qi",
               .width = c(.80,.95),
               alpha=0.7) +
  labs(title = 'Posterior distributions for population-level\neffects in Model M1i_ca',
       x = "time bin", 
       y = "logit-ca") +
  scale_fill_brewer(palette = "Dark2") +
  scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
  scale_y_continuous(limits=c(-10,10)) +
  theme(axis.text.x = element_text(angle=90)) +
  facet_wrap(~condition)
p_tidy_fixed_ca
```

@@

```{r epred-grand-plot}
 p1 <- ggplot(epreds_grand, aes(x=timebin, y=.epred, 
                          fill=prime, color=prime)) +
    stat_lineribbon(aes(linetype=prime),
                    point_interval="median_qi",
                    alpha = 0.5, 
                    .width = c(.8,.95)) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,1)) +
    labs(x = "time bin", y = "predicted conditional accuracy") #+
    #ggtitle("Average participant")
p1
```

@@

```{r plot-epred-pid}
p2 <- ggplot(epreds_pid, aes(x=timebin, y=.epred, 
                       fill=prime, color=prime)) +
    stat_lineribbon(aes(linetype=prime),
                    point_interval="median_qi",
                    alpha = 0.5, 
                    .width = c(.8,.95)) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,1)) +
    labs(x = "time bin", y = "predicted conditional accuracy") +
   # ggtitle("Each participant (N = 6)") +
    facet_wrap(~pid, ncol=3)
p2
```

@@

```{r grand-ame-plot}
p11 <- ggplot(epreds_grand_diffs, aes(x=timebin, y=diff_ca, 
                       fill=contrast)) +
  stat_lineribbon(alpha = 0.5, 
                  point_interval = "mean_qi",
                  .width=c(.8,.95)) +
  geom_hline(yintercept = 0, 
             color = "red", 
             lty = 3) +
  scale_y_continuous(limits=c(-1,1)) +
  scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
  scale_fill_manual(values=c("#D95F02FF", "#7570B3FF")) +
  theme(axis.text.x = element_text(angle=90)) +
  labs(x = "time bin", y = "difference in predicted ca") +
  facet_wrap(~contrast)
p11
```

@@

```{r epred-pid-ame}
epreds_pid_diffs <- epreds_pid %>%
  pivot_wider(id_cols = c(pid,timebin, .draw),
              names_from = "prime",
              values_from = ".epred") %>% #80000 x 5
  mutate(`congruent minus blank` = congruent - blank,
         `incongruent minus blank` = incongruent -  blank) %>% 
  select(-c(blank,congruent,incongruent)) %>% 
  pivot_longer(cols = c(`congruent minus blank`,`incongruent minus blank`),
               names_to = "contrast",
               values_to = "diff_ca") 
epreds_pid_diffs # 160 000 rows 
```

@@

```{r epred-pid-ame-plot}
p22 <- ggplot(epreds_pid_diffs, aes(x=timebin, y=diff_ca, 
                       fill=contrast, color=contrast)) +
    stat_lineribbon(aes(linetype=contrast),
                    alpha = 0.5, 
                    point_interval = "mean_qi",
                    .width=c(.8,.95)) +
    #stat_halfeye(point_interval = "mean_qi",.width=c(.8,.95)) +
    geom_hline(yintercept = 0, color = "red", lty = 3) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(-1,1)) +
    labs(x = "time bin", y = "difference in predicted ca") +
   # ggtitle("Subject-specific AMEs") +
    facet_wrap(~pid, ncol=3)
p22
```

@@

(p_tidy_fixed_ca / p1 / p11) +
    plot_annotation(tag_levels = 'A') +
   # plot_layout(guides = "collect",
  #              axes = "collect_x") & 
    theme(legend.position = "bottom")

```

>>>>

# plot
p_tidy_fixed_ca <- ggplot(tidy_fixed_ca, aes(x = timebin, y = value, fill=condition)) +  
  stat_halfeye(point_interval = "median_qi",
               .width = c(.80,.95),
               alpha=0.7) +
  labs(title = 'Posterior distributions for population-level\neffects in Model M1i_ca',
       x = "time bin (upper bound in ms)", 
       y = "logit-ca") +
  scale_fill_brewer(palette = "Dark2") +
  scale_x_discrete(labels = c(6:15)*40, breaks = 6:15) +
  scale_y_continuous(limits=c(-10,10)) +
  theme(axis.text.x = element_text(angle=90)) +
  facet_wrap(~condition)
p_tidy_fixed_ca
```

@@

```{r epred-grand-plot}
 p1 <- ggplot(epreds_grand, aes(x=timebin, y=.epred, 
                          fill=prime, color=prime)) +
    stat_lineribbon(aes(linetype=prime),
                    point_interval="median_qi",
                    alpha = 0.5, 
                    .width = c(.8,.95)) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = c(6:15)*40, breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,1)) +
    labs(x = "time bin (upper bound in ms)", 
         y = "predicted conditional accuracy")

p1
```

@@

```{r plot-epred-pid}
p2 <- ggplot(epreds_pid, aes(x=timebin, y=.epred, 
                       fill=prime, color=prime)) +
    stat_lineribbon(aes(linetype=prime),
                    point_interval="median_qi",
                    alpha = 0.5, 
                    .width = c(.8,.95)) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = c(6:15)*40, breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,1)) +
    labs(x = "time bin (upper bound in ms)", 
         y = "predicted conditional accuracy") +
    facet_wrap(~pid, ncol=3)
p2
```

@@

```{r grand-ame-plot}
p11 <- ggplot(epreds_grand_diffs, aes(x=timebin, y=diff_ca, 
                       fill=contrast)) +
  stat_lineribbon(alpha = 0.5, 
                  point_interval = "mean_qi",
                  .width=c(.8,.95)) +
  geom_hline(yintercept = 0, 
             color = "red", 
             lty = 3) +
  scale_y_continuous(limits=c(-1,1)) +
  scale_x_discrete(labels = c(6:15)*40, breaks = 6:15) +
  scale_fill_manual(values=c("#D95F02FF", "#7570B3FF")) +
  theme(axis.text.x = element_text(angle=90)) +
  labs(x = "time bin (upper bounds in ms)", 
       y = "difference in predicted ca") +
  facet_wrap(~contrast)

p11
```

@@

```{r epred-pid-ame}
epreds_pid_diffs <- epreds_pid %>%
  pivot_wider(id_cols = c(pid,timebin, .draw),
              names_from = "prime",
              values_from = ".epred") %>% #80000 x 5
  mutate(`congruent minus blank` = congruent - blank,
         `incongruent minus blank` = incongruent -  blank) %>% 
  select(-c(blank,congruent,incongruent)) %>% 
  pivot_longer(cols = c(`congruent minus blank`,`incongruent minus blank`),
               names_to = "contrast",
               values_to = "diff_ca")

epreds_pid_diffs  
```

@@

```{r epred-pid-ame-plot}
p22 <- ggplot(epreds_pid_diffs, aes(x=timebin, y=diff_ca, 
                       fill=contrast, color=contrast)) +
    stat_lineribbon(aes(linetype=contrast),
                    alpha = 0.5, 
                    point_interval = "mean_qi",
                    .width=c(.8,.95)) +
    geom_hline(yintercept = 0, color = "red", lty = 3) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = c(6:15)*40, breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(-1,1)) +
    labs(x = "time bin (upper bound in ms)", 
         y = "difference in predicted ca") +
    facet_wrap(~pid, ncol=3)
p22
```

@@

(p_tidy_fixed_ca / p1 / p11) +
    plot_annotation(tag_levels = 'A') +
    theme(legend.position = "bottom")
```
